Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-05 contents/introduction.tex

\item Annotating with regards to consistent landmarks is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person. Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks. For example human ears have very complicated inner structures (e.g. helix, crus antihelicis, scapha, tragus, lobe etc.) which differ remarkably between ears. Moreover, certain ear parts, such as  fossa triangularies and crus helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation. Another example is human body which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints. The task of annotation was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT). Unfortunately, these annotations are, in many cases, not consistent\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot by any means be compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:intro}). As it was also pointed out recently \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.

@@

After establishing dense shape correspondences, we describe how dense Active Appearance Models (AAMs) can be built on top of that. We show that the proposed methodology can be applied for landmark localisation, even though not tailored for that task, achieving particularly good performance. We demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks. Furthermore, We show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence. We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods [..]. Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for different body parts.

>>>>

\item Annotating with regards to consistent landmarks is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person. Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks. For example human ears have very complicated inner structures (e.g. helix, crus antihelicis, scapha, tragus, lobe etc.) which differ remarkably between ears. Moreover, certain ear parts, such as  fossa triangularies and crus helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation. Another example is human body which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints. The task of annotation was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT). Unfortunately, these annotations are, in many cases, not consistent\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot by any means be compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:wrong_anno}). As it was also pointed out recently \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.

@@

After establishing dense shape correspondences, we describe how dense Active Appearance Models (AAMs) can be built on top of that. We show that the proposed methodology can be applied for landmark localisation, even though not tailored for that task, achieving particularly good performance. We demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks. Furthermore, We show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence. We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods \cite{pfister2015flowing}. Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for different body parts.
